MSDS6372Project2

### 2021-04-10 MSDS6372Project2.Rmd
bug fix

#### Objective 2 part 3 - Nonparametric model approach - Random forest
- Default RF ntree = 500 and m variables =sqrt(p) seem to work better than ntree=100
- Try iterate through mtry variable from 1 to 10 using prediction cut off previously discovered - seems mtry = 1 works best on overall accuracy
- After actually fitting random forest with mtry = 1 the AUC = 0.882 (performance is worse compare to default mtry=3). Sensitivity and Specificity also suffers after adjusting the cut off. So Default RF option still wins!
- So Mtry = 3 seems to be the perfect balance for our dataset in order to provide good AUC.
- We further added in calculations for AUC under each mtry #, and it also tells us mtry=3 provides the best AUC value
> overall.Accuracy
 [1] 0.8526934 0.8479922 0.8114267 0.7909892 0.7781913 0.7676787 0.7533790 0.7478289 0.7484166 0.7407770
> overall.auc
 [1] 0.882 0.903 0.907 0.903 0.899 0.893 0.890 0.887 0.883 0.878
```{r}
library(randomForest)
set.seed(1)
# By default use sqrt(p) number variables when building a random forest of classification trees
rf.adult = randomForest(income~.,data=adult)

>>>>

#### Objective 2 part 3 - Nonparametric model approach - Random forest
- Default RF ntree = 500 and m variables =sqrt(p) seem to work better than ntree=100
- Try iterate through mtry variable from 1 to 10 using prediction cut off previously discovered - seems mtry = 1 works best on overall accuracy
- After actually fitting random forest with mtry = 1 the AUC = 0.882 (performance is worse compare to default mtry=3). Sensitivity and Specificity also suffers after adjusting the cut off. So Default RF option still wins!
- So Mtry = 3 seems to be the perfect balance for our dataset in order to provide good AUC.
- We further added in calculations for AUC under each mtry #, and it also tells us mtry=3 provides the best AUC value
> overall.Accuracy
 [1] 0.8526934 0.8479922 0.8114267 0.7909892 0.7781913 0.7676787 0.7533790 0.7478289 0.7484166 0.7407770
> overall.auc
 [1] 0.882 0.903 0.907 0.903 0.899 0.893 0.890 0.887 0.883 0.878

```{r}
library(randomForest)
set.seed(1)
# By default use sqrt(p) number variables when building a random forest of classification trees
rf.adult = randomForest(income~.,data=adult)
